---
title: 'Study 2: Reinforcement-Punishment Analysis'
author: "Debbie Yee"
date: "3/18/2018"
output: pdf_document
---

# Study 2: Within-Subjects Reinforcement and Punishment Effects of Liquid and Monetary Incentives
This is an analysis of the subject performance of study 2 of reinforcement and punishment effects of liquid feedback with monetary gains and losses. In the study, subjects perform the cued task-switching paradigm, where they have classify a letter (vowel/consonant) or digit (odd/even). During the baseline runs, they don't receive any feedback and are told to respond "as quickly and accurate as possible." During the incentive runs, they receive a drop of liquid (2 mL) to indicate successful attainment of monetary reward in a single trial. Each subject performs 6 incentive runs: 3 reinforcement (all liquids and monetary gains) and 3 punishment avoidance (all liquids and avoidance of monetary losses). Liquids are blocked. \newline

Criterion RT is calculated on subject performance during the baseline run (30%), and is the same for both reinforcement and punishment conditions.

# Loading relevant packages
```{r packages, message=FALSE}
library(ggplot2)
library(gridExtra)
library(dplyr)
library(tidyr)
library(lme4)
library(lmerTest)
library(sjPlot)
source("/Users/debbieyee/Dropbox/CCPLabProjects/Liquid_Feedback/OAYA_Combined/Analysis/Yee/summarySEwithin2.R")
```

# Path directories of data input/output
```{r}
# data directories
data.path<-paste0("/Users/debbieyee/Dropbox/CCPLabProjects/Liquid_Feedback/",
                  "Reinforce-Punish_Combined/Study2/Data/SubjectData/TrimmedData/",
                  "Study2_ConsolidatedRewardData.csv")
runkey.path<-paste0("/Users/debbieyee/Dropbox/CCPLabProjects/Liquid_Feedback/",
                    "Reinforce-Punish_Combined/Study2/Data/SubjectData/TrimmedData/",
                    "Study2_ConsolidateRunKey.csv")
figure.path<-paste0("/Users/debbieyee/Dropbox/CCPLabProjects/Liquid_Feedback/",
                    "Reinforce-Punish_Combined/Study2/Analysis/Figures/")
```

# Format the data for analysis
```{r}
# Read in the data
data<-read.csv(data.path,header = TRUE)
runkey<-read.csv(runkey.path, header = TRUE) 

# Formatting incentive data
data<-select(runkey) 
```

